\documentclass[12pt,letterpaper]{article}
\usepackage{preamble}

\newcommand\course{GENETIS}
\newcommand\hwnumber{July 2023}

\begin{document}
\tableofcontents

% June 1
\section{Sat}
\subsection{HPol Loop}
\begin{enumerate}
  \item Started working on HPol loop locally,
    will regularly push to Github.
\end{enumerate}

% June 2
\section{Sun}
\subsection{HPol Loop}
\begin{enumerate}
  \item Working on HPol loop part A.
  \item TODO: learn about git "submodule" (for "Shared-Code/GA")
  \item From
    \url{https://stackoverflow.com/questions/17683458/how-do-i-commit-case-sensitive-
    only-filename-changes-in-git}, regarding Github file name change:\\
    "git mv -f yOuRfIlEnAmE yourfilename"
\end{enumerate}

% June 3
\newpage
\setcounter{section}{3}

% June 4
\section{Tue}
\subsection{HPol Work}
\subsubsection{GA}
\begin{enumerate}
  \item Back to going through the GA c++ files.
  \item There has to be a way to improve "DataRead()". The file currently has an "if" 
    check inside a "for" loop, probably not the most efficient way to do this.
\end{enumerate}

% June 5
\newpage
\setcounter{section}{5}

% June 6
\section{Thu}
\subsection{HPol Work}
\subsubsection{GA: DataRead.h}
\begin{enumerate}
  \item Finished modifying "DataRead.cpp" and pushed to Github.
  \item The part that reads "fitnessScores.csv" inside "DataRead.cpp" only reads the 
    first column. \textbf{TODO:} figure out what the second column of "fitnessScores.csv"
    is (in PAEA there are three columns actually)
\end{enumerate}

% June 7
\newpage
\setcounter{section}{7}

% June 8
\section{Sat}
\subsection{HPol Work}
\subsubsection{GA: Sort.h}
\begin{enumerate}
  \item Started modifying Sort.h.
\end{enumerate}

% June 9
\section{Sun}
\subsection{HPol Work}
\subsubsection{GA: Sort.h}
\begin{enumerate}
  \item "original_location" and "t" are probably not needed at all? Check again and
    get rid of these.
  \item Actually not sure where we obtain "parent_location". It doesn't seem like
    "DataRead.h" provides this vector. And the whole "original_location"-stuff just 
    seems weird. Is this part of the program incomplete?
\end{enumerate}

% June 10
\section{Mon}
\subsection{HPol Work}
\subsubsection{GA: Sort.h}
\begin{enumerate}
  \item Finished editing "Sort.h" and pushed to Github.
  \item Will discuss the issue mentioned in yesterday's log during the meeting today.
\end{enumerate}

\subsection{Monday's Meeting}
\begin{enumerate}
  \item From Ezio, regarding creating a remote "hpol" branch and allowing others to 
    review the changes:
    \begin{quote}
    you can push your local branch with ``git push origin your-branch'' and it
    will show you a link to create the PR on GitHub. Once you create the PR you
    can keep adding commits to the branch and push them and it will update the PR.
    \end{quote}
\end{enumerate}

% June 11
\section{Tue}
\subsection{Git}
\begin{enumerate}
  \item A good video explaining how to squash git commits using "git rebase -i <#>"\\
    \url{https://www.youtube.com/watch?v=RwvTrSm7zEY}
\end{enumerate}
\subsection{HPol Work}
\subsubsection{GA: Sort.h}
\begin{enumerate}
  \item \st{Will test today if this still produce the desired result since I removed
    the vector \texttt{original\_location} and int \texttt{t} yesterday.}
  \item tested the above; the script works just fine.
  \item Following Ezio's advice, stop making extraneous changes on the HPol branch.
    Will make a patch branch to poke at and destroy and leave HPol alone until XF 
    work is more or less done.
\end{enumerate}
\subsection{Clean Work}
\begin{enumerate}
  \item Started a new branch based on "Hpol" (base commit is "HPol Pause") called
    "clean" locally. I will use this branch for my own understanding, possibly cleaning
    up the scripts as I go over them.
  \item From Ezio, regarding the workflow of GENETIS (in a closed pull-request at
    \url{https://github.com/osu-particle-astrophysics/Shared-Code/pull/24})
    \begin{quote}
   1 create a local branch with some commits\\
   2 push the branch on GitHub (git push origin your-branch) and create a PR
   (it gives you a link to create it after the push)\\
   3 wait for reviews and comments\\
   4 add more commits to the local branch to address the reviews/comments\\
   5 push them to GitHub (git push origin your-branch, without
   forcing/squashing/rebasing) -- the PR will update automatically to include
   the new commit\\
   6 repeat steps 3-5 until the PR is approved\\
   7 click on the squash merge button on GitHub to merge the PR on main\\
    \end{quote}
    
\end{enumerate}

% June 12
\section{Wed}
\subsection{HPol Work}
\subsubsection{Loop}
\begin{enumerate}
  \item Looking into the various "Part_B1" scripts and the corresponding batch job.
\end{enumerate}

% June 13
\section{Thu}
\subsection{HPol Work}
\subsubsection{Loop}
\begin{enumerate}
  \item Finished cleaning up "Part_B1"
  \item Setting up HPol skeleton for "Part_B1"
  \item Fixed Part A GA call error (when design is bicone)
  \item Now using submodules for "Shared-Code" (more info in HPol repo's readme).
  \item Started looking into "Part_B2"
\end{enumerate}
% June 14
% June 15
% June 16
% June 17
% June 18
% June 19
% June 20
% June 21
% June 22
% June 23
% June 24
% June 25
% June 26
% June 27
% June 28
% June 29
% June 30
% June 31

\end{document}
